{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/paper.tex
massive restructuring, split results by fiducial and variations
Updates from Overleaf
rearrange appendix to 2col, move mw compare
make the discussion make sense again
update numbers
updates to 3.1 and 3.2 from Selma
ensure all stats are up to date
change title to two lines, fix names

\documentclass[twocolumn]{aastex63}
\received{\today}
\shorttitle{Detecting DCOs with LISA}
\graphicspath{{../figures/}}

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}
\usepackage{xcolor} % to add more color options

@@

\newcommand{\BHBHFourYear}{36}
\newcommand{\BHNSFourYear}{33}
\newcommand{\NSNSFourYear}{8}
\newcommand{\BHBHTenYear}{56}
\newcommand{\BHNSTenYear}{55}
\newcommand{\NSNSTenYear}{13}

\newcommand{\BHBHNotWDWDFour}{15}
\newcommand{\BHNSNotWDWDFour}{10}
\newcommand{\NSNSNotWDWDFour}{4}
\newcommand{\BHBHNotWDWDTen}{22}
\newcommand{\BHNSNotWDWDTen}{17}
\newcommand{\NSNSNotWDWDTen}{7}

\newcommand{\BHBHDistinguishedFour}{5}
\newcommand{\BHNSDistinguishedFour}{4}
\newcommand{\NSNSDistinguishedFour}{3}
\newcommand{\BHBHDistinguishedTen}{11}
\newcommand{\BHNSDistinguishedTen}{7}
\newcommand{\NSNSDistinguishedTen}{5}

@@

% \color{white}
% \pagecolor{black}

@@

% selma's newest catchy one
\title{Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA}

% selma suggested removing BHNS
% \title{Predictions for neutron star and black hole binaries with LISA}

% original
%\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}

@@

\author[0000-0002-4421-4962]{F. Broekgaarden}
\affiliation{\cfa}

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{\mpa}
\affiliation{\UvA}
\affiliation{\cfa}

@@

\keywords{LISA, black hole, neutron star, binary}

@@

\section{Results} \label{sec:results}
\input{sections/results.tex}

@@

\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions. This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728. We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}

>>>>

\documentclass[twocolumn, twocolappendix]{aastex63}
\received{\today}
\shorttitle{Detecting DCOs with LISA}
\graphicspath{{../figures/}}

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}
\usepackage{xcolor} % to add more color options
\usepackage{wrapfig}

@@

\newcommand{\BHBHFourYear}{74}
\newcommand{\BHNSFourYear}{42}
\newcommand{\NSNSFourYear}{8}
\newcommand{\BHBHTenYear}{TODO}
\newcommand{\BHNSTenYear}{TODO}
\newcommand{\NSNSTenYear}{TODO}

% number of systems that are definitely not WDWDs
\newcommand{\BHBHNotWDWDFour}{33}
\newcommand{\BHNSNotWDWDFour}{16}
\newcommand{\NSNSNotWDWDFour}{5}
\newcommand{\BHBHNotWDWDTen}{TODO}
\newcommand{\BHNSNotWDWDTen}{TODO}
\newcommand{\NSNSNotWDWDTen}{TODO}

% percentage of systems above Chandrasekhar mass
\newcommand{\BHBHAboveMaxWDWDFourPerc}{17}
\newcommand{\BHNSAboveMaxWDWDFourPerc}{21}
\newcommand{\NSNSAboveMaxWDWDFourPerc}{3}
\newcommand{\BHBHAboveMaxWDWDTenPerc}{TODO}
\newcommand{\BHNSAboveMaxWDWDTenPerc}{TODO}
\newcommand{\NSNSAboveMaxWDWDTenPerc}{TODO}

% number of systems that can be determined as either a BH or NS
\newcommand{\BHBHEitherBHOrNSFour}{11}
\newcommand{\BHNSEitherBHOrNSFour}{6}
\newcommand{\NSNSEitherBHOrNSFour}{3}
\newcommand{\BHBHEitherBHOrNSTen}{TODO}
\newcommand{\BHNSEitherBHOrNSTen}{TODO}
\newcommand{\NSNSEitherBHOrNSTen}{TODO}
\newcommand{\BHBHEitherBHOrNSFourPerc}{14}
\newcommand{\BHNSEitherBHOrNSFourPerc}{13}
\newcommand{\NSNSEitherBHOrNSFourPerc}{35}
\newcommand{\BHBHEitherBHOrNSTenPerc}{TODO}
\newcommand{\BHNSEitherBHOrNSTenPerc}{TODO}
\newcommand{\NSNSEitherBHOrNSTenPerc}{TODO}

% percentage of systems in lower mass gap
\newcommand{\BHBHLowerMassGap}{35\%}
\newcommand{\BHNSLowerMassGap}{38\%}

% percentage of systems with q > 0.8
\newcommand{\BHBHqAbovePointEight}{8\%}
\newcommand{\BHNSqAbovePointEight}{0\%}
\newcommand{\NSNSqAbovePointEight}{90\%}

% percentage of systems with e > 0.01
\newcommand{\BHBHNotCirc}{86\%}
\newcommand{\BHNSNotCirc}{47\%}
\newcommand{\NSNSNotCirc}{86\%}

% percentage of systems with e > 0.3
\newcommand{\BHBHHighlyEccentric}{22\%}
\newcommand{\BHNSHighlyEccentric}{8\%}
\newcommand{\NSNSHighlyEccentric}{12\%}

% percentage of systems with something other than 1 detectable harmonic
\newcommand{\BHBHMultipleHarmonicsFourPerc}{55}
\newcommand{\BHNSMultipleHarmonicsFourPerc}{28}
\newcommand{\NSNSMultipleHarmonicsFourPerc}{66}
\newcommand{\BHBHMultipleHarmonicsTenPerc}{TODO}
\newcommand{\BHNSMultipleHarmonicsTenPerc}{TODO}
\newcommand{\NSNSMultipleHarmonicsTenPerc}{TODO}

% percentage of systems with >1 harmonic and in disc
\newcommand{\BHBHEccInDiscFourPerc}{40}
\newcommand{\BHNSEccInDiscFourPerc}{25}
\newcommand{\NSNSEccInDiscFourPerc}{60}
\newcommand{\BHBHEccInDiscTenPerc}{TODO}
\newcommand{\BHNSEccInDiscTenPerc}{TODO}
\newcommand{\NSNSEccInDiscTenPerc}{TODO}

% percentage of systems with fractional chirp mass uncertainty < 1
\newcommand{\BHBHChirpMassMeasureable}{20}
\newcommand{\BHNSChirpMassMeasureable}{17}
\newcommand{\NSNSChirpMassMeasureable}{4}

@@

% Milky Way notation
\newcommand{\achem}{\ensuremath{[\alpha/\mathrm{Fe}]}}

@@

\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA}}

@@

\author[0000-0002-4421-4962]{F.S. Broekgaarden}
\affiliation{\cfa}

\author[0000-0001-9336-2825]{S.E. de Mink}
\affiliation{\mpa}
\affiliation{\UvA}
\affiliation{\cfa}

@@

\keywords{LISA, gravitational waves, black hole, neutron star, binary}

@@

\section{Results I - Fiducial} \label{sec:results}
\input{sections/results.tex}

\section{Results II - Model variations} \label{sec:variations}
\input{sections/variations.tex}

@@

\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions. TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project. This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728. We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}
